Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2022-03-02 Supplemental-Material-B-Annotated-Analysis.Rmd
forest plots added

summary of regression results from the aggregated contact and interaction quality data.

@@

@@

summary of mixed models results of the contemporaneous contact effects.

@@

@@

(a) Core Need Fulfillment predicting Interaction Quality.   
(b) Core Need Fulfillment predicting Outgroup Attitudes.   
(c) Core Need Fulfillment and Interaction Quality predicting Outgroup Attitudes.

@@

@@

(a) Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).  
(b) Core Need Fulfillment predicting Outgroup Attitudes, while controlling for self-determination theory needs (intergroup contact sample).

@@

>>>>

@@

![Summary of regression results from the aggregated contact and interaction quality data.](Figures/forestParametricGeneralLm.png)

@@

@@

![Summary of mixed models results of the contemporaneous contact effects.](Figures/forestParametricFEGeneralLmer.png)

@@

@@

![Core Need Fulfillment predicting Interaction Quality.](Figures/forestParametricFETheoryQualityCore.png)

![ore Need Fulfillment predicting Outgroup Attitudes.](Figures/forestParametricFETheoryAttitudeCore.png)

![Core Need Fulfillment and Interaction Quality predicting Outgroup Attitudes.](Figures/forestParametricFETheoryAttitudeCoreQuality.png)

@@

@@

![Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).](Figures/forestParametricFERobustContact.png)

![Core Need Fulfillment predicting Outgroup Attitudes, while controlling for self-determination theory needs (intergroup contact sample).](Figures/forestParametricFERobustSDT.png)
